---
title: "Bootstrap para datos funcionales"
output: html_notebook
---

#Bootstrap para datos simulados

```{r, echo=FALSE}
library(fda.usc)
library(pracma)

fdata.bootstrap2 <-function(fdataobj, E, ts, statistic=func.mean,alpha=0.05,nb=200,
                           smo=0.0,draw=FALSE,draw.control=NULL,...){
  if (!is.fdata(fdataobj)) fdataobj=fdata(fdataobj)
  data<-fdataobj[["data"]]
  estmues<-statistic(fdataobj,...)
  nr<-nrow(fdataobj)
  nc<-ncol(fdataobj)
  tt =fdataobj[["argvals"]]
  rtt=fdataobj[["rangeval"]]
  names=fdataobj[["names"]]
  distboot<-matrix(NA,nrow=nb)
  estboot<-matrix(NA,nrow=nb,ncol=nc)
  pb=txtProgressBar(min=0,max=nb,style=3)
  for (i in 1:nb){
    setTxtProgressBar(pb,i-0.5)
    bmuestra<-fdataobj[sample(1:nr,size=nr,replace=TRUE),]
    if (smo>0) {
      bmuestra[["data"]]<-bmuestra[["data"]]+mvrnorm(n=nr,rep(0,nc),var(data)*smo)
    }
    stat<-statistic(bmuestra,...)
    estboot[i,]<-stat[["data"]]
    setTxtProgressBar(pb,i)
  }
  close(pb)
  center<-estmues
  #for (i in 1:nb){  aux<-fdata(estboot[i,],tt,rtt)
  #  distboot[i]<-metric.lp(center,aux,...)  }
  #print(dim(distboot))
  distboot<-metric.lp(fdata(estboot,tt,rtt),center,...)
  dist<-max(distboot[rank(distboot)<=floor((1-alpha)*nb)])
  resample<-fdata(estboot,tt,rtt,names)
  if (draw){
    if (is.null(draw.control)) draw.control=list("col"=c("grey","blue","pink"),"lty"=c(2,1,1),"lwd"=c(1,2,1))
    if (is.null(draw.control$lwd)) draw.control$lwd=c(1,2,1)
    if (is.null(draw.control$lty)) draw.control$lty=c(2,1,1)
    if (is.null(draw.control$col)) draw.control$col=c("grey","blue","pink")
    plot(fdataobj,lwd=draw.control$lwd[1],lty=draw.control$lty[1],col=draw.control$col[1])
    lines(resample[distboot<=dist],lwd=draw.control$lwd[3],lty=draw.control$lty[3],col=draw.control$col[3])
    lines(estmues,lwd=draw.control$lwd[2],lty=draw.control$lty[2],col=draw.control$col[2])
    lines(ts, E1, lwd=4, lty=1)
    legend(x=min(tt),y=0.99*max(data),legend=c("original curves",stat$names$main,"bootstrap curves IN", "m(t)"),
           lty=c(1,1,1,1),lwd=c(1,4,1,4), col=c("grey","blue","red", "black"), cex=0.6,box.col=0)
  }
  return(list("statistic"=estmues,"dband"= dist,"rep.dist"=distboot,
              "resample"=resample,fdataobj=fdataobj))
}

fdata.bootstrap3 <-function(fdataobj, E, ts, statistic=func.mean,alpha=0.05,nb=200,
                            smo=0.0,draw=FALSE,draw.control=NULL,...){
  if (!is.fdata(fdataobj)) fdataobj=fdata(fdataobj)
  data<-fdataobj[["data"]]
  estmues<-statistic(fdataobj,...)
  nr<-nrow(fdataobj)
  nc<-ncol(fdataobj)
  tt =fdataobj[["argvals"]]
  rtt=fdataobj[["rangeval"]]
  names=fdataobj[["names"]]
  distboot<-matrix(NA,nrow=nb)
  estboot<-matrix(NA,nrow=nb,ncol=nc)
  pb=txtProgressBar(min=0,max=nb,style=3)
  for (i in 1:nb){
    setTxtProgressBar(pb,i-0.5)
    bmuestra<-fdataobj[sample(1:nr,size=nr,replace=TRUE),]
    if (smo>0) {
      bmuestra[["data"]]<-bmuestra[["data"]]+mvrnorm(n=nr,rep(0,nc),var(data)*smo)
    }
    stat<-statistic(bmuestra,...)
    estboot[i,]<-stat[["data"]]
    setTxtProgressBar(pb,i)
  }
  close(pb)
  center<-estmues
  distboot<-metric.lp(fdata(estboot,tt,rtt),center,...)
  dist<-max(distboot[rank(distboot)<=floor((1-alpha)*nb)])
  resample<-fdata(estboot,tt,rtt,names)
  if (draw){
    if (is.null(draw.control)) draw.control=list("col"=c("grey","blue","pink"),"lty"=c(2,1,1),"lwd"=c(1,2,1))
    if (is.null(draw.control$lwd)) draw.control$lwd=c(1,2,1)
    if (is.null(draw.control$lty)) draw.control$lty=c(2,1,1)
    if (is.null(draw.control$col)) draw.control$col=c("grey","blue","pink")
    #plot(fdataobj,lwd=draw.control$lwd[1],lty=draw.control$lty[1],col=draw.control$col[1])
    plot(resample[distboot<=dist],lwd=draw.control$lwd[3],lty=draw.control$lty[3],col=draw.control$col[3])
    lines(estmues,lwd=draw.control$lwd[2],lty=draw.control$lty[2],col=draw.control$col[2])
    lines(ts, E, lwd=4, lty=1)
    legend(x=0,y=1,legend=c(stat$names$main,"bootstrap curves IN", "Var(t)"),
           lty=c(1,1,1),lwd=c(1,4,4), col=c("red","blue","black"), cex=0.5,box.col=0)
  }
  return(list("statistic"=estmues,"dband"= dist,"rep.dist"=distboot,
              "resample"=resample,fdataobj=fdataobj))
}

```

Primero, veamos una muestra de tamaño 100 los modelos (1) y (2):

```{r}
kNs <- 100
#100 equidistant points (ts = timesteps).
kNc <- 100
# Number of curves.
ts <- linspace(0, 1, n = kNs) 
# Initialize covariance matrix for first e(t) with zeroes.
cov.e <- matrix(rep(0, len=kNs*kNs), nrow=kNs, ncol=kNs)
# Initializ covariance matrix for h(t) with zeroes.
cov.h <- matrix(rep(0, len=kNs*kNs), nrow=kNs, ncol=kNs) 
E1 <- numeric(kNs) 
# Fill up covariances and expected values as described in the paper.
for (i in 1:kNs) {
  E1[i] <- 10*ts[i]*(1-ts[i])
  for (j in 1:kNs) {
    cov.e[i,j] <- exp(-(abs(ts[i] - ts[j]))/0.3)
    cov.h[i,j] <- min(ts[i], ts[j])
  } 
}
mu <- numeric(kNs)
e.S0 <- mvrnorm(n = kNc, mu=mu, Sigma=cov.e) 
# Sample 1 to 5 error, first three with error e(t), last two with error h(t).
e.S1 <- mvrnorm(n = kNc, mu=mu, Sigma=cov.h)
S0 <- sweep(e.S0, 2, E1, "+")
S1 <- sweep(e.S1, 2, E1, "+")
A <- fdata(S0, ts)
B <- fdata(S1, ts)
plot(A)

```
```{r}
plot(B)
```

Ahora, vamos a considerar 

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
